When, why, and how to avoid, prefer, or tolerate inbreeding

### 2018-04-02 presentation/inbreeding.Rmd
New slides, almost done

@@

>>>>

- Offspring produced ($n$) decreases with investment per offspring ($m$)
- Offspring viability ($\upsilon$) increases with investment per offspring
- Highest rate of viable offspring production defines optimal parental investment ($m^{*}$)
- Optimally investing parents produce $W = n \times \upsilon^{*}$ offspring

## Synthesis of inbreeding and parental investment

<center>
![](images/In_PI_1.png)
</center>

<span style="font-size: 18px;">
1. Duthie, AB et al. (2016) *Proc. R. Soc. B* [**282**:20161845](https://bradduthie.github.io/DuthieEtAl2016c.pdf). <br>
</span>

## Synthesis of inbreeding and parental investment

<center>
![](images/In_PI_2.png)
</center>

<span style="font-size: 18px;">
1. Duthie, AB et al. (2016) *Proc. R. Soc. B* [**282**:20161845](https://bradduthie.github.io/DuthieEtAl2016c.pdf). <br>
</span>

## Synthesis of inbreeding and parental investment

<center>
![](images/In_PI_3.png)
</center>

<span style="font-size: 18px;">
1. Duthie, AB et al. (2016) *Proc. R. Soc. B* [**282**:20161845](https://bradduthie.github.io/DuthieEtAl2016c.pdf). <br>
</span>

## Synthesis of inbreeding and parental investment

<center>
![](images/In_PI_4.png)
</center>

<span style="font-size: 18px;">
1. Duthie, AB et al. (2016) *Proc. R. Soc. B* [**282**:20161845](https://bradduthie.github.io/DuthieEtAl2016c.pdf). [SI-1](https://bradduthie.github.io/DuthieEtAl2016c_SI.pdf) <br>
</span>

## Synthesis of inbreeding and parental investment

<center>
![](images/In_PI_5.png)
</center>

<span style="font-size: 18px;">
1. Duthie, AB et al. (2016) *Proc. R. Soc. B* [**282**:20161845](https://bradduthie.github.io/DuthieEtAl2016c.pdf). [SI-1](https://bradduthie.github.io/DuthieEtAl2016c_SI.pdf) <br>
</span>

@@

## Acknowledgements

## General conclusions {.smaller}

**Predict selection for an allele causing inbreeding avoidance or preference when:**

**Females should mate multiply to adjust inbreeding given:**

**Multiple factors affecting how to avoid inbreeding, including:**

- Direct costs on pre- versus post-copulatory inbreeding avoidance
- Polyandry modulates selection on pre- versus post-copulatory inbreeding avoidance

**Increased mate relatedness and inbreeding depression will cause optimal parental investment to increase**
